Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-26 paper/paper.tex
update

Anglican can be mostly implemented as a regular programming
language, except for the handling of these checkpoints.
Depending on the \textit{inference algorithm}, \texttt{sample}
and \texttt{observe} may result in implicit input/output
operations and control changes. For example, \texttt{observe} in
particle filtering inference algorithms \cite{WVM14} is a non-deterministic
control statement at which a thread (also called particle) 
can be either forked or terminated. Similarly, in 
Metropolis-Hastings \cite{WSG11},
\texttt{sample} is both an input
statement which `reads' values from a random source,
and a non-deterministic control statement
(with delayed effect), eventually affecting acceptance or
rejection of a sample.

>>>>

Anglican can be mostly implemented as a regular programming
language, except for the handling of these checkpoints.
Depending on the \textit{inference algorithm}, \texttt{sample}
and \texttt{observe} may result in implicit input/output
operations and control changes. For example, \texttt{observe} in
particle filtering inference algorithms \cite{WVM14} is a non-deterministic
control statement at which a particle (corresponding to
a thread executing a program)
can be either replicated or terminated. Similarly, in 
Metropolis-Hastings \cite{WSG11},
\texttt{sample} is both an input
statement which `reads' values from a random source,
and a non-deterministic control statement
(with delayed effect), eventually affecting acceptance or
rejection of a sample.
